Solving two-person zero-sum sequential games via efficient computation of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker

### 2014-10-30 neurobreakfast.tex
more tex

\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage[labelformat=empty, labelsep=none,
  font=footnotesize]{caption}
\usepackage{sidecap}
\usecolortheme[named=Bittersweet]{structure}
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{stmaryrd}

\usepackage{bm}
\setbeamercovered{transparent}

@@

\title[NeuroBreakfast - \today\hspace{\stretch{1}}
  (\insertframenumber{}/\inserttotalframenumber{})]{Solving two-person zero-sum sequential games
via efficient computaion of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker}
\author{DOHMATOB Elvis \inst{1,2}}
\institute{
  \inst{1}Parietal Team, INRIA\\\inst{2}Universit\'e Paris-Sud}

@@

\begin{frame}
  \frametitle{Two-person zero sum Sequential games}
  \uncover<1->{
  \begin{itemize}[<+->]
      \item There are 3 players: \textcolor{blue}{nature (player 0)}, \textcolor{red}{Alice (player 1)}, and \textcolor{green}{Bob (player 2)}.}
    \item Players take turns in making moves
    \item Set of moves of any two distinct players don't
      overlap (i.e \textcolor{red}{$A_p \cap A_q = \emptyset$ if $p \ne q$})
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Minimax NE problem for general sequential game}
  \begin{equation}
    \underset{x \in Q_1}{maximize}\text{ }\underset{y \in \mathbb{R}_+^m, Fy=f}{minimize}\text{ }y^TAx,
  \end{equation}

\uncover<2>{
  where:
  \begin{equation}
    \left .
    \begin{split}
      Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex}, and}\\
      Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
    \end{split}
    \right\}
  \end{equation}
}
\end{frame}

>>>>

\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage[labelformat=empty, labelsep=none,
  font=footnotesize]{caption}
\usepackage{sidecap}
\usecolortheme[named=Bittersweet]{structure}
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{bm}
\setbeamercovered{transparent}

@@

\title[NeuroBreakfast - \today\hspace{\stretch{1}}
  (\insertframenumber{}/\inserttotalframenumber{})]{Solving two-person zero-sum sequential games
via efficient computation of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker}
\author{DOHMATOB Elvis \inst{1,2}}
\institute{
  \inst{1}Parietal Team, INRIA\\\inst{2}Universit\'e Paris-Sud}

@@

\begin{frame}
  \frametitle{Two-person zero sum Sequential games}
  \uncover<1->{
  \begin{itemize}[<+->]
      \item There are 3 players: \textcolor{blue}{nature (player 0)}, \textcolor{red}{Alice (player 1)}, and \textcolor{green}{Bob (player 2)}.}
    \item Players take turns in making moves
    \item Sets of moves of any two distinct players don't
      overlap (i.e \textcolor{red}{$A_p \cap A_q = \emptyset$ if $p \ne q$})
  \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Strategy profiles, simplexes and complexes}
\begin{definition}
  \begin{itemize}[<+->]
    \item The \textcolor{blue}{$n$-\textit{simplex}}, denoted $\Delta_n$, is the subset of $\mathbb{R}^{n+1}$ defined by
      \begin{equation}
        \Delta_n := \left\{x \in \mathbb{R}^{n+1}\text{ }|\text{ } x_i \ge 0\text{ } \forall i, \text{ and } \sum_{i=1}^{n+1}{x_i} = 1\right\}
      \end{equation}
    \item Each kink $\delta_i := (0, ..., 0,1,0, ...,0)$ of $\Delta_n$ represents a \textit{\textcolor{blue}{pure-strategy}}.
      Any non-kink point $x$ of $\Delta_n$ represents a
      \textit{\textcolor{blue}{mixed-strategy}}. Thus $\Delta_n$ is simply the \textit{convex hall} of $(n+1)$-dimensional pure strategies $\delta_i$.
    \item A \textit{\textcolor{blue}{complex}} is an abstract \textit{\textcolor{blue}{polyhedron}} whose kinks are themselves simplexes. Points on
      a complex correspond to \textit{\textcolor{blue}{behavioural strategies}}.
  \end{itemize}
\end{definition}
\end{frame}

\begin{frame}
\frametitle{Simplexes and complexes (examples of)}
\begin{figure}
  \includegraphics[width=3cm]{simplex.png}
  \includegraphics[width=3cm]{7-simplex.png}
  \includegraphics[width=3cm]{10-simplex.png}
  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
\end{figure}
\end{frame}

\begin{frame}
  \frametitle{NE minimax and best-response in sequential-games}
Thanks to the sequence-form representation, we have:
\begin{itemize}[<+->]
\item NE problem for Alice and Bob is the the \textit{\textcolor{blue}{saddle-point problem}}
  \begin{equation}
    \underset{x \in Q_1}{maximize}\text{ }\underset{y \in Q_2}{minimize}\text{ }y^TAx,
    \label{eq:minimax_stengel}
  \end{equation}

  \uncover<2>{
    where:
   \begin{equation}
     \left .
     \begin{split}
       Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex, and}}\\
       Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
     \end{split}
      \right\}
   \end{equation}
   A saddle-point $(x^*, y^*)$ corresponds to a NE for the game.
   \item Given a fixed behavioural strategy $y_0 \in Q_2$ for Bob, a \textit{\textcolor{blue}{best-response}} behavioural strategy $x_0$ for Alice
     \footnote{Of course, there is an analogous concept for Bob.}
    is a solution to the LCP
    \begin{equation}
      \underset{x\in Q_1}{maximize}\text{ }{y_0^TAx}
    \end{equation}
}
  \end{itemize}
\end{frame}
